Streaming Fact Extraction for Wikipedia Entities at Web-Scale

### 2013-11-18 paper/flairs27/content/abstract.tex
Update abstract.tex

Wikipedia.org is the largest online resource for free information and maintained by a small number of volunteer editors.
Because of its large size, information on some pages can easily be neglected and can easily become out of date.
To address the issues of stale articles we create a system that is able to read
in a stream in a web of diverse documents from across the web and recommend
facts to be added to specified Wikipedia pages.
We developed a three-stage stream system to create models of entities,
filter out irrelevant documents and 
extract facts from documents mentioning entities.
The systems over a 4.5 TB web document corpus data set over 16 months and 139 Wikipedia pages.
Our results show a promising framework for fact extraction from arbitrary web pages for Wikipedia pages.

>>>>

Wikipedia.org is the largest online resource for free information and is maintained by a small number of volunteer editors.
Because of its large size, information on some pages can easily be neglected and can easily become out of date.
To address the issues of stale articles we create a system that is able to read
in a stream in a web of diverse documents from across the web and recommend
facts to be added to specified Wikipedia pages.
We developed a three-stage stream system to create models of entities,
filter out irrelevant documents and 
extract facts from documents mentioning entities.
The systems over a 500 million web document corpus data set over 16 months and 139 Wikipedia pages.
Our results show a promising framework for fact extraction from arbitrary web pages for Wikipedia pages.
